% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
    {Jan 2021}   {Software Architect | Tech Lead | Design Authority}{Foursys}{Brazil}
    {Present} {
                      \begin{itemize}
                        \item Member of the Design Authority Chapter, creating, validating and documenting project templates and archetypes that will be used organization-wide by other developers.
                        \item Tech Lead for a Javascript/Angular micro-frontend based architecture.
                        \item Code Reviewer and Feedback coach for developers.
                        \item Technical Writer, contributed to dozens of Confluence articles.
                        \item Created a developer recruitment/onboarding pipeline using organization-wide OKRs and KPIs, providing hiring/training metrics on Power BI.                          
                      \end{itemize}
                    }
                    {Leadership, Java, Node JS, Express, Angular, Maven, Bamboo, Nexus}
  \emptySeparator
  \experience
    {Apr 2019} {Software Architect | Client Delivery }{VanHack}{Remote}
    {Nov 2020}    {
                      \begin{itemize}
                        \item Developed a Java based BPMN Integration solution for the HR Industry         
                        \item Created integrations for hiring/termination/background-check/payroll/tax connecting ADP, Taleo, Success Factors, Gr8People, Bullhorn, Lever, Gupy and others.
                        \item Direct relationship with clients. As part of the delivery team, I was involved in collecting and understanding requirements, documenting and communicating with the clients, UAT testing and deployment to production.          
                      \end{itemize}
                    }
                    {Java, JBoss EAP, Maven, Activiti BPMN, Docker, Jenkins}
  \emptySeparator
  \experience
    {Jul 2017}     {Software Consultant}{Accenture}{Brazil}
    {Apr 2019}    {
                      \begin{itemize}
                        \item On-site consultancy to financial institutions.
                        \item Legacy Technology Migration (Cobol to Java microsservices)
                        \item Worked on a proprietary design system using Adobe XD + Angular 14
                        \item Managed cluster of Java microsservices using Docker Swarm             
                        \item Managed devops pipeline with Jenkins to Azure Cloud
                        \item Managed APIs with WSO2 Middleware          
                        \item Developed an MVP for a decentralized mortgage system leveraging BPMN and Blockchain.
                      \end{itemize}
                    }
                    {Java, Cobol, Angular, Jenkins, Ansible, Docker, WSO2, Camunda, Kibana, New Relic}
  \emptySeparator
  \experience
    {Sep 2016}     {Software Architect | Delivery}{Crossover}{Remote}
    {May 2017}    {
                      \begin{itemize}
                        \item Remote consultancy for Versata Software.
                        \item Worked on the delivery team of the Quantum Retail ERP.
                        \item Created Apache Kafka brokers and consumers.
                        \item Managed client's environment in a multi-tenant architecture.
                        \item Created Database Migrations on Oracle.
                        \item Created shell scripts using bash to provide automation for feature testing and deployment  
                        \item Created a Graphql API with web-hook features
                      \end{itemize}
                    }
                    {Java, Kafka, Rabbit MQ, Linux, Bash, Oracle, Graphql}
  \emptySeparator
  \experience
    {Feb 2015}     {CTO}{Epitrack}{Brazil}
    {Mar 2016}    {
                      \begin{itemize}
                        \item Technical Leadership
                        \item Led development for the implementation of the innovative participatory surveillance and digital epidemiology research project focused on Zika, Dengue Fever and Chikungunya diseases.
                        \item Led development for the \website{https:////outbreaksnearme.org/us/en-US}{Flu Near You} website in partnership with the Skol Foundation, Boston Chidren's Hospital and Harvard Medical School
                        \item Led the development of the \website{https:////play.google.com/store/apps/details?id=com.guardioesapp&hl=pt_BR&gl=US}{Guardians Of Health} app for participatory surveillance during the 2016 Brazillian Olympics
                        \item Led the planning and execution of \website{https:////www.youtube.com/watch?v=SzLGD2MBV34}{Epihack Rio 2015} the largest Hackaton event in epidemiology!
                        \item Represented Brazil in the Forum of Participatory Surveillance and Pandemics 2015 created by the USDA-FDA
                      \end{itemize}
                    }
                    {Leadership, Javascript, Angular, Node JS, PHP, Python, R}
  \emptySeparator
  \experience
    {Jan 2012}     {Lead Innovation Developer}{Ogilvy}{Brazil}
    {Jul 2014}    {
                      \begin{itemize}
                        \item Technical Leadership
                        \item Led the Flash/Motion teams working with Actionscript for Advertising/Display Media
                        \item Led development of the \website{http:////www.shakemelikeascroll.com/happinessrefill/}{Coca Cola Happiness Refill App}. Receiver of a 2012 Bronze Cannes Lions Award on the Mobile category.
                        \item Led the development of the \website{https:////www.youtube.com/watch?v=SC6MRmLaAGc}{Hellmann's Recipe Receipt} project, a recipe creator embedded on cashier prints. Receiver of the 2012 Gold Cannes Lions Award on the Direct category.
                      \end{itemize}
                    }
                    {Leadership, Flash, Actionscript, Javascript, WebGL, Java, Android, C++ (Open Frameworks)}
  \emptySeparator
  \experience
    {May 2007}     {Flash Developer}{Cappen}{Brazil}
    {Apr 2011}    {
                      \begin{itemize}
                        \item Created websites and rich internet applications using Flash
                        \item Created a custom Actionscript 3 Framework focused on website design and motion
                        \item Created touchscreen totems and point of sale interactive demonstrations using Flash
                        \item Backend development using PHP
                      \end{itemize}
                    }
                    {Flash, Actionscript, Javascript, PHP}
  \emptySeparator
\end{experiences}
